\section{Inline}
\subsection{Citations}
\begin{itemize} 
\item cite: \cite{2016}, multiple: \cite{2016,Einstein_1922}
\item citet: \citet{2016}, multiple: \citet{2016,Einstein_1922},
\item citep: \citep{2016}, multiple: \citep{2016,Einstein_1922}, 
\item with page numbers \cite[pp.~2]{2016}, \cite[pp.~12-22]{Einstein_1922}
\end{itemize}

\subsection{Labels and references}\label{sec:labels}
Examples of references: 
\begin{itemize}
\item Subsection~\ref{sec:labels},
\item Figure~\ref{fig:example},
\item Equation~\ref{eq:lorenz}, and eq.~\ref{eq:coins}
\item Table~\ref{table:example}
\end{itemize}

\subsection{Block quotes}
\subsubsection{{\LaTeX} \{quote\}}
\begin{quote}
I do not like them in a box.
I do not like them with a fox.
I do not like them in a house.
I do not like them with a mouse.
I do not like them here or there.
I do not like them anywhere.
I do not like green eggs and ham.
I do not like them, Sam-I-am.
\end{quote}

\subsubsection{{\LaTeX} \{verbatim\}}
\begin{verbatim}
I do not like them in a box.
I do not like them with a fox.
I do not like them in a house.
I do not like them with a mouse.
I do not like them here or there.
I do not like them anywhere.
I do not like green eggs and ham.
I do not like them, Sam-I-am.
\end{verbatim}

\subsubsection{{\LaTeX} \{lstlisting\}}
\begin{lstlisting}
I do not like them in a box.
I do not like them with a fox.
I do not like them in a house.
I do not like them with a mouse.
I do not like them here or there.
I do not like them anywhere.
I do not like green eggs and ham.
I do not like them, Sam-I-am.
\end{lstlisting}

\subsection{Footnotes}
Example of a footnote\footnote{this one but also\footnote{a nested note}} and one more\footnote{that one}.

\subsection{Sub/superscripts}
In text we have textsuperscript\textsuperscript{sup} and textsubscript\textsubscript{sub}.

In math we have the hat $x^2$ and the underscore $x_2$.

\subsection{Math equations}
The Lorenz Equations (numbered, labeled as eq:lorenz and eq:coins):
\begin{eqnarray}\label{eq:lorenz}
\dot{x} & =\sigma(y-x)\nonumber  \\ 
\dot{y} & =\rho x-y-xz\nonumber  \\ 
\dot{z} & =-\beta z+xy\nonumber \\
\end{eqnarray}

The probability of getting \(k\) heads when flipping \(n\) coins is:
\begin{equation}\label{eq:coins}
P(E) = {n \choose k} p^k (1-p)^{ n-k}
\end{equation}


\subsubsection{Inline and display style}

We can say inline that for any $x \in \mathcal{N}$ we know that display style (unnumbered):
$$ x \geq 0 $$

\subsection{Code listings}
\begin{lstlisting}
\documentclass{article}
% document preamble
\begin{document}
% document body
Hello World!
\end{document}
\end{lstlisting}

\subsection{Links}
\begin{itemize}
\item A simple \verb|\url|: \url{https://www.authorea.com}
\item An abbreviated \verb|\href|: \href{https://www.authorea.com}{Authorea homepage}
\end{itemize}